### 2016-01-18 papers/CAFe/HIPS-paper/intro.tex
Added text on synchonization

Since each CAF process executes the same program, there are no good avenues for exploiting
task-based parallelism.  Neither is there a mechanism for dynamic coarray memory
allocation, nor a mechanism for the remote execution of functions.  In CAF, like MPI, the
programmer often combines distributed memory processes running the same program image with a
shared memory threaded programming model using OpenMP (or OpenACC).  This model breaks down
when dealing with architectures that are not isomorphic to the model for which MPI and
relatives were designed -- a distributed collection of homogenous processing elements in
which each processing element supports a small number of parallel threads of execution.  For
example, an HPC system that makes use of traditional multicore CPUs as well as GPGPU accelerators
breaks this model and, to effectively program it, currently requires a mixture of programming
systems in a single application.

In this paper we propose CAFe: \emph{Co-Array Fortran Extensions}.  These extensions to CAF introduce
relatively minor additions to the existing coarray portion of the Fortran language.  They
include the concept of subimages in order to nest coarray images, semantics for distributed
array declarations, memory placement, remote memory transfer, and remote task execution.  CAFe
builds upon the existing standardized coarray features of Fortran.  We will introduce the
CAFe extensions that are proposed to define their semantics, demonstrate their use in simple
examples, and provide experimental results demonstrating their performance in a prototype implementation.
CAFe is complementary to
previous work extending coarray Fortran\cite{mellor-crummey:2009:caf2,jin:2011:caf2}.

>>>>

Since each CAF process executes the same program, there are no good avenues for exploiting
task-based parallelism.  Neither is there a adequate mechanism for dynamic coarray memory
allocation, nor a mechanism for the remote execution of functions.  In CAF, like MPI, the
programmer often combines distributed memory processes running the same program image with a
shared memory threaded programming model using OpenMP (or OpenACC).  This model breaks down
when dealing with architectures that are not isomorphic to the model for which MPI and
relatives were designed -- a distributed collection of homogenous processing elements in
which each processing element supports a small number of parallel threads of execution.  For
example, an HPC system that makes use of traditional multicore CPUs as well as GPGPU accelerators
breaks this model and, to effectively program it, currently requires a mixture of programming
systems in a single application.

In this paper we propose CAFe: \emph{Co-Array Fortran Extensions}.  These extensions to CAF introduce
relatively minor additions to the existing coarray portion of the Fortran language.  They
include the concept of subimages in order to nest coarray images, semantics for distributed
array declarations, memory placement, remote memory transfer, and remote task execution
and synchronization.  CAFe
builds upon the existing standardized coarray features of Fortran.  We will introduce the
proposed CAFe extensions, define their semantics, demonstrate their use in simple
examples, and provide experimental results demonstrating their performance in a prototype implementation.
CAFe is complementary to
previous work extending coarray Fortran\cite{mellor-crummey:2009:caf2,jin:2011:caf2}.
